|

### 2023-05-01 paper.Rmd
0 -> 20 selections

In each lineup evaluation, the participant was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, participants were permitted to select zero plots without providing the reason. No participant was shown the same lineup twice. Information about preferred pronouns, age group, education, and previous experience in visual experiments were also collected. A participant's submission was only included in the analysis if the data plot is identified for at least one attention check. <!--Data of rejected submissions are discarded automatically to maintain the overall data quality.-->

>>>>

In each lineup evaluation, the participant was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots are from others. If there is no noticeable difference between plots in a lineup, participants had the option to select zero plots without the need to provide a reason. During the process of recording the responses, a zero selection was considered to be equivalent to selecting all 20 plots. No participant was shown the same lineup twice. Information about preferred pronouns, age group, education, and previous experience in visual experiments were also collected. A participant's submission was only included in the analysis if the data plot is identified for at least one attention check. <!--Data of rejected submissions are discarded automatically to maintain the overall data quality.-->
